### 2017-11-15 paper/mechanism.tex
backup

\begin{lstlisting}[emph={Assign, Process, Apply}, emphstyle=\color{blue}, numbers=none, escapechar=\%, language=Python, caption=Graph Processing Kernel]
GraphKernel (A, P, iterations) :
  for_each iterations
    x := Assign(P)
  	y := Process(A,x)
  	P := Apply(y)	  
  end_for

Incoming Edges := GraphKernel(A, identity, 1):
	with Assign(P)    := P
	     Process(A,x) := A * x
	     Apply(y)     := y
\end{lstlisting}

>>>>

\begin{lstlisting}[emph={Assign, Process, Apply}, emphstyle=\color{blue}, numbers=none, escapechar=\%, language=Python, caption=Graph Processing Kernel]
GraphKernel (G, P, iterations) :
  for_each iterations
    x := Assign(P)
  	y := Process(G,x)
  	P := Apply(y)	  
  end_for

e.g.: 
	FindIncomingEdges (A, identity, 1):
	with Assign(P)    := P
	     Process(A,x) := A * x
	     Apply(y)     := y
\end{lstlisting}
